03_traitement

### 2019-12-17 r/03_traitement.Rmd
gg_contingence_freq (plot des crosstables) + début vizu traitement par crosstable
gg_contingence_freq (finie)
afdm

@@

>>>>

```{r}
library("FactoMineR") 
library("factoextra")
```

```{r}
df<- data_sel %>% filter(dataset=="train")
res_famd <- FAMD(df[-c(1:3)], graph = FALSE)
saveRDS(object = res_famd,
      file = "./../data/res_famd.rds")
```

```{r}
res_famd<-readRDS("./../data/res_famd.rds")
```

```{r}
eig_val<-get_eigenvalue(res_famd)
head(eig_val)
```

```{r}
fviz_famd_var(res_famd,repel = F)
```

@@

```{r}
liste_var_factor = type_col[type_col == "factor"]
```

```{r}
for (var in names(liste_var_factor)[2:length(liste_var_factor)]){
    print(gg_contingence_freq(get("var")))
}
```
